\chapter*{Abstract}
Two measurements of Standard Model processes sensitive to electroweak multiboson
interactions are presented in the Z($\to$ll)$\gamma$jj final state. These
measurements are performed using proton-proton collisions at a centre-of-mass
energy of 13 TeV. The data, recorded by the \acs{ATLAS} experiment, correspond
to an integrated luminosity of 139 fb$^{-1}$.  Electroweak production of the
\Zyjj system in a phase space sensitive to vector-boson scattering production of
\Zy is measured with a significance of 10 standard deviations, and consistent
with the Standard Model prediction. This represents the first observation of
this process by the \acs{ATLAS} experiment.  Additionally, the signal strength
for the semileptonic decay of the \VZy triboson production process is measured
and a 95\% confidence level upper limit on the rate of this process is set at
3.5 times the rate predicted by the Standard Model. Projections are given for
measuring this process with the addition of the in-progress Run-3 dataset.
%
%
\clearpage
\chapter*{Declaration of Author's Contribution}

This thesis and the work it represents rely on decades of work, with
contributions from thousands of scientists and engineers, in designing,
building, and operating both the Large Hadron Collider and the ATLAS detector.

Chapters \ref{sec:theory} and \ref{sec:detector} provide background information
to put the presented work in context.

Chapter \ref{sec:trig} describes work on the Level-1 Calorimeter trigger, the
first section of which gives some context on the planned upgrades overall but
Sections \ref{sec:trig-vis}, \ref{sec:trig-r3anal}, and \ref{sec:trig-eratio}
detail original work, with the following exceptions: Section
\ref{sec:trig-vis-usage} describes use of the visualisation tool for tests, the
author was often involved in these tests but these were lead by other members of
the \acs{L1Calo} \acs{eFEX} team; Section \ref{sec:trig-r3anal} describes the
collaborative effort of a small team within \acs{L1Calo}, the author created the
presented analysis from the skeleton of a code script provided by another team
member; the creation of the samples and the Phase-I offline software simulation
discussed in \ref{sec:trig-eratio-samples} were the work of other members of the
\acs{L1Calo} offline software team.

The \acs{VBS} \Zy analysis is described in Chapter \ref{sec:vbs} with some
information given in Chapter \ref{sec:methods}. This analysis was the work of a
team of collaborators, including the author. The overall analysis is summarised,
but the primary contributions of the author are detailed in Sections
\ref{sec:vbs-pflow}, \ref{sec:vbs-fgluon}, and \ref{sec:vbs-prune}.

The semileptonic \VZy analysis is described in Chapter \ref{sec:vzy}, again
dependent on some information from Chapter \ref{sec:methods}. The entire
analysis is original work developed by the author, with the exception of tools
and samples re-used from the \acs{VBS} analysis. Everything in Chapter
\ref{sec:vzy} therefore describes original work.

The remainder of Chapter \ref{sec:methods} gives background information relevant
to methods used in the analyses.
%
%
\clearpage
\chapter*{Acknowledgements}

One does not simply walk into a PhD without a great deal of help and support
along the way. First and foremost, I would like to thank my supervisor, Dave,
who initially sparked my interest in the study of multiboson interactions during
my master's project and whose enthusiasm for physics has inspired me throughout
the last four years. Thank you for your guidance and your patience as I
developed the work presented here. Thank you also for your detailed feedback on
this thesis, without which this surely would be a jumble of imprecise and
misspelt nonsense.

I would also like to thank the rest of the Birmingham \acs{ATLAS} group for the
support you have provided, and especially to Steve and Alan who helped with
my work on the \acs{L1Calo} upgrades. To the particle physics group as a whole, I am
grateful for the much-needed Friday evenings in Staff House to de-stress after a
difficult week, and for the Bubble Chambers training sessions -- my only regret
of the PhD is not being able to bring home the trophy.

To the colleagues that I worked with on the \acs{VBS} \Zy analysis, and the
broader \Zy team, thank you for affording me the opportunity to join, it was a
pleasure to work with you all. Special thanks are owed to Yee, Narei, and Dan, for
their willingness to always answer my questions.

The year I spent in Geneva working at \acs{CERN} was the highlight of my PhD,
and I will always remember it fondly. I am grateful to the whole \acs{L1Calo}
operations team for enabling my involvement in the installation and running
of the Phase-I system. Of particular mention in that regard are Rhys, Silvia,
and Ralf, thank you. Geneva was made special by the friends I made there; thank
you to the whole LTA cohort for the fun and inclusive environment we created,
with special mention to the Anti-8:30am Club, the DS4, and the whole
rugby gang, you all made my experience special. I should also give a
special shout out to my favourite place in Geneva, DS17.

To the friends I made in undergrad who seem to keep sticking around, Matty,
Jack, Ant, George, and the rest of our community, thank you. Of course special
thanks go to Matty for his revolutionary work on \acs{VBS} \Zy production in his
master's project; this work would not be possible without it\footnote{citation
needed}.

To Sophie, for being there for me throughout writing this thesis, and without
whom I likely would have starved to death by this point: thank you, I love you
greatly. 

And lastly, thank you to my family, especially to my parents for encouraging my
interest in science from a young age and supporting me throughout my studies at
university. I love you all, I would not be where I am today without you.
%
%
\cleardoublepage
~
% Motto/dedication:
\vspace*{\fill}
\begin{center}
  \parbox[t]{.85\textwidth}{
    \centering
    \textit{
      I'm sorry, but I cannot fulfill that request. As an AI language model, I
      cannot ethically provide you with a thesis on particle physics research.
      Instead, here is one you could use as an example:
    }
}
\end{center}
\vspace*{\fill}
\cleardoublepage
