% ========== MONTE CARLO PREDICTIONS ==========

The \ac{SM} is tested by comparing its predicted cross-sections for a set of
measurable physics processes with the rate observed in data. To isolate
processes of interest, this is often done in complicated phase spaces and
differentially across distributions, so calculating the predicted cross-sections
is quite complex. Real measurements are also subject to the limitations and
effects of the detector; for accurate comparisons to be made between data and
predictions, these need to be accounted for.

The solution to this problem is to generate Monte Carlo (\acsfirst{MC}) events
representing the \ac{SM} prediction. For a given final state (i.e. the set of
particles produced in the interaction) a sample of events is generated for each
contributing process, containing particles with random kinematic properties
generated in such a way that the overall distribution matches the expectation
from the model. If all processes are accounted for, taking the sum of events
from all of these samples in the desired phase space gives an estimate for the
\ac{SM} prediction; this is then compared to data to see if the measurement
agrees with the theory.

%Talk about specific generators
Production of \ac{MC} samples is a very complicated process and there are
several implementations commonly used in the field, known as
\ac{MC} generators. Generators discussed in this thesis include \madgraph
\cite{madgraph5amc}, \sherpa \cite{sherpa2dot2}, \pythia \cite{pythia8dot2},
\powheg \cite{powheg}, and \herwig \cite{herwigpp}.

% PDFs
These generators are used to simulate the hard scatter, the interaction
responsible for creating the desired final state. In order to match the
simulation to the conditions under which the process is initiated, the generator
must use a \ac{PDF} set determined from data under the same conditions.

% What needs to be added to hard scatter?
Simulating a single physics process does not give a complete picture of a real
detector event, however. This is the core of the hard scatter, the primary high
energy collision in the event, but several additional steps must be taken:
parton showering, applied to any strongly interacting particles; hadronisation,
converting these showers into composite hadrons; adding the `underlying event',
all of the activity expected in the collision from sources other than the hard
scatter; and detector simulation, accounting for effects of particles being
measured by the detector.

% parton showering and hadronisation: pythia and herwig
For each parton from the hard-scatter process, a shower of \ac{QCD} activity is
produced from repeated strong interactions. This continually creates more, lower
energy, partons until the energies reach a regime where confinement effects
become relevant. Confining the shower products into colourless hadrons is
handled by a hadronisation model, such as string fragmentation
\cite{Andersson1983}. Both parton showering and hadronisation are incorporated
into \ac{MC} event generators. Some generators, such as \sherpa, will simulate
the hard-scatter process, parton showering, and hadronisation all in one. In
other cases the hard-scatter process is created with one generator, e.g.
\madgraph, and then another generator is used to add parton showering and
hadronisation to it, e.g. \pythia or \herwig.

% merging and resummation scales
The models used to simulate these processes are not calculable from first
principles and have parameters that can be adjusted to best describe observed
physics. These parameters include merging and resummation scales, describing the
merging of jets from the parton shower and the hard scatter event and the
resummation of soft gluon emissions \cite{sherpa2dot2}.

% what is the underlying event? Modelling issues => 
% tuning parameters to data to match underlying event description
Underlying event is a term used to describe everything happening around the hard
scatter in collisions; this includes spectator and pileup interactions, as
introduced in Section \ref{sec:theory-pp}.
%This includes interactions from pileup collisions, other
%proton-proton collisions in the event besides the one that produced the hard
%scatter, and spectator interactions, i.e. interactions between partons in the
%same protons as the hard scatter.
Modelling the underlying event is very dependent on the specific conditions
under which the collisions are happening.  This is mitigated by tuning certain
parameters of the model to match data; different `tunes' are available from data
collected under different conditions.  For \ac{MC} samples, underlying event
modelling is typically handled by the same generators as the parton showering
and hadronisation.

% detector simulation
Having simulated the hard scatter, parton showering, hadronisation, and the
underlying event, the particles and their kinematics should be established. The
remaining step is determining how this event would be detected in an experiment,
if it were from a real collision. For the \acs{ATLAS} detector (introduced in
Section \ref{sec:detector-atlas}) this is done using \geantfour \cite{geant4,
ATLASsim1}.

% truth and reco information in MC samples
A distinction is made between information from \ac{MC} samples before and after
detector simulation. Simulated events before detector simulation is applied are
known as `truth' events, they contain only the physics processes and are not
subject to any inefficiencies or misidentification of the simulated detector.
Events completing the full simulation chain are known as reconstructed \ac{MC}
events. These are typically linked so that the truth properties (or `truth
record') of reconstructed \ac{MC} events are accessible. Analysis is typically
done using reconstructed \ac{MC} events, but in certain cases making
distinctions based on truth information is necessary.

% Link into my analyses?
Events simulated in the manner discussed here are used extensively for the two
analyses presented in this thesis (as well as for studies presented in Chapter
\ref{sec:trig}). The signal process and all backgrounds in the final state have
dedicated \ac{MC} simulation samples generated in order to model the kinematics
of events. Generation of these specific samples is discussed in Section
\ref{sec:methods-samples}.
