% ====== Template Fit Section ======

The signal strength, $\mu_\text{EW}$, is used to parametrise the fiducial
cross-section for the signal process, $\sigma^\text{EW}$, where
%
\begin{equation*}
  \mu_\text{EW} = \sigma^\text{EW}_\text{meas} / \sigma^\text{EW}_\text{exp},
\end{equation*}
%
i.e. the ratio of the measured cross-section to the \ac{SM} expectation. This
signal strength is extracted from the data with a maximum likelihood fit,
performed on $m_{jj}$ distributions in the \ac{SR} and \ac{CR} simultaneously.
\ac{MC} distributions for backgrounds and signal are used as templates, with
normalisations for the signal and \ac{QCD} \Zy background allowed to float in
the fit.

The bin size of the $m_{jj}$ distribution used for the fit is chosen to optimise
the statistical significance of data in each bin. Electron and muon channels are
treated together, using the sum of events from both for all aspects of the fit.
Likelihood functions are built for each bin of the $m_{jj}$ distribution in both
the \ac{SR} and \ac{CR} using a Poisson distribution, and these are all combined
to form a single extended likelihood

Systematic uncertainties are included in the fit as Gaussian nuisance
parameters. The effect of each uncertainty on the normalisation and shape of the
$m_{jj}$ distribution is considered individually and a pruning system, described
in Section \ref{sec:vbs-prune}, is used to reduce the number of nuisance
parameters needed.

The fit extracts the value of the signal strength for the signal process,
$\mu_\text{EW}$. From this a significance of the measurement, under the null
hypothesis of $\mu_\text{EW}=0$, can be extracted using the likelihood-ratio
test. If the significance is greater than five standard deviations of a
Gaussian, it is considered to be observed as an excess over the background-only
hypothesis. The value of the signal strength can also be used to give a
measurement of the fiducial cross-section of the process, given the of the
\ac{SM} expectation of this cross-section, calculated from the nominal \ac{MC}:
%
\begin{equation*}
  \sigma_\text{EW}^\text{exp} = 4.73
  \pm 0.01 \, (\text{stat.})
  \pm 0.15 \, (\acs{PDF})
  ^{+0.23} _{-0.22} \, (\text{scale})
  ~\text{fb}.
\end{equation*}
