% ====== Event selection section ======

Event selection is applied to simulation, using the samples detailed in Section
\ref{sec:methods-samples}, and to data, as specified in Section
\ref{sec:methods-data}, to reach the desired \ac{VBS}-enhanced phase
space. Cuts are first made to the \Zy system following the prescription given in
Section \ref{sec:methods-selection}.

% TODO write about b-tagging in object reconstruction
Imposing \ac{VBS}-like kinematics on the jets further reduces the phase space.
Jets are required to have a transverse momentum of at least 50 GeV, and a
rapidity of less than 4.4 in magnitude. There must be at least two jets, and no
b-tagged jets in the event. The dijet system, formed from the two highest
momentum jets, should have a mass $m_{jj} > 150$ GeV and an inter-jet separation
of $|\Delta y_{jj}| > 1.0$. A veto on `gap jets', jets
(reconstructed with $p_T > 25$ GeV) found in the rapidity region between the two
VBS tag jets, is applied to exploit the difference between VBS jets and
colour-connected \ac{QCD} jets. A loose cut is placed on the centrality of the
$ll\gamma$ system relative to the jets, $\zeta(ll\gamma) < 5$, where centrality
is given by
%
\begin{equation}
  \zeta(ll\gamma) = \left|
                      \frac { y_{ll\gamma} - (y_{j_1} + y_{j_2})/2}
                            { y_{j_1} - y_{j_2} }
                    \right|,
  \label{eqn:vbs-selection-centrality}
\end{equation}
%
where $y_{ll\gamma}$ is the rapidity of the $ll\gamma$ system and $y_{j_i}$ is
the rapidity of the $i$\textsuperscript{th} highest-energy jet.

These cuts define the analysis region, and are summarised in Table
\ref{tab:vbs-selection}.  This is further split into the \ac{SR} and the
\ac{QCD} \ac{CR} with tighter requirements on the $ll\gamma$ centrality:
$\zeta(ll\gamma) < 0.4$ defines the \ac{SR} and $\zeta(ll\gamma) > 0.4$ gives
the \ac{CR} used for the \QCDZy background estimate.

\begin{table}[p]
  \centering
  \renewcommand\arraystretch{1.1}
  % VBS selection table:
  \caption{
    Summary of event selection criteria defining the \acs{VBS} analysis region.
    This region is further subdivided by additional criteria on
    $\zeta(ll\gamma)$.
  }
  \label{tab:vbs-selection}
  \begin{tabular}{p{6em}l}
    \midrule\midrule
    \multicolumn{2}{c}{VBS \Zy selection} \\
    \midrule
    \Zy system & \Zy selection (Table \ref{tab:anacom-zy-selection}) \\
    \midrule
    Jet & $N_j \geq 2$ \\
        & $|y_j| < 4.4$ \\
        & $p_T^{j} > 50$ GeV \\
        & $N_j^\text{b-tag} = 0$ \\
        & $N_j^\text{gap} = 0$ \\
    \midrule
    Dijet system & $m_{jj} > 150$ GeV \\
                 & $|\Delta y_{jj}| > 1$ \\
    \midrule
    Event & $\zeta(ll\gamma) < 5$ \\
    \midrule\midrule
  \end{tabular}
  \\[2cm]
  % Fiducial selection table:
  \caption{
    Particle-level selection applied to events in the fiducial region. Included
    are approximate particle-level equivalents to the photon isolation
    and overlap removal applied for the signal region selection.
  }
  \label{tab:vbs-selection-fiducial}
  \begin{tabular}{p{6em}l}
    \midrule\midrule
    \multicolumn{2}{c}{VBS \Zy fiducial selection} \\
    \midrule
    Lepton & $p_T^{l,1} > 30$ GeV,
             $p_T^{l,2} > 20$ GeV \\
           & $|\eta_l| < 2.47$,
             $N_l \geq 2$ \\
    \midrule
    Photon & $E_T^\gamma > 25$ GeV,
             $|\eta_\gamma| < 2.47$ \\
           & $E_T^\text{cone20} < 0.07E_T^\gamma$ \\
           & $\Delta R(l,\gamma) > 0.4$ \\
    \midrule
    Jet    & $p_T^{j} > 50$ GeV, 
             $|y_j| < 4.4$ \\
           & $N_j \geq 2$ \\
           & remove jets if $\Delta R(\gamma,j) < 0.4$ \\
           & or if $\Delta R(l,j) < 0.3$ \\
    \midrule
    Event  & $m_{ll} > 40$ GeV \\
           & $m_{ll}+m_{ll\gamma} > 182$ GeV \\
           & $m_{jj} > 150$ GeV \\
           & $|\Delta y_{jj}| > 1$ \\
           & $N_j^\text{gap} = 0$,
             $\zeta(ll\gamma) < 0.4$ \\
    \midrule\midrule
  \end{tabular}

\end{table}

\subsection{Fiducial region definition}

As the result of this analysis is a fiducial cross-section measurement, the
particle-level selection for which this measurement applies, i.e. the fiducial
region, must be defined.  This fiducial selection mimics the detector-level
selection for the \ac{SR} as closely as possible. Table
\ref{tab:vbs-selection-fiducial} reports this selection. For more details of the
exact parameters defining this fiducial region, see Reference \cite{VBSZy-CONF}.
